\bf Title here

### 2022-11-17 project/PaperTemplate/paper.Rmd
Add some files
Edit on paper

authors: 
- name: XX YOUR NAME HERE XX
  thanks: The authors gratefully acknowledge ...
  affiliation: Department of Mathematics and Statistics, Amherst College

@@

abstract: |
  The text of your abstract.  200 or fewer words. It is intended to provide an overview of your paper and may be similar to your synopsis. Note that an abstract can only include one paragraph in this format. You may want to put your synopsis here as you work to refer to it easily.

@@

>>>>

authors: 
- name: Justin Papagelis
  thanks: The authors gratefully acknowledge ...
  affiliation: Department of Mathematics and Statistics, Amherst College

@@

abstract: |
  For my project, I plan to explore different bootstrap methods for creating confidence intervals and then perform comparisons between a couple of the methods. My paper will re-introduce the idea of bootstrap to my peers and give some background on constructing confidence intervals. We will also go deeper into the theory behind the construction of confidence intervals from bootstrapped data. These various methods to create a confidence interval from a bootstrap can include the percentile method, bias-corrected method, accelerated method, and the studentized method, as well as others. I will demonstrate how these bootstrap methods work using “toy examples,” which will be datasets in which a specific bootstrap method is appropriate. To demonstrate my understanding of the methods, I will write a simulation to compare a few of them and determine how they perform against each other. I will show my understanding of the different methods of creating confidence intervals from bootstrapped data by communicating the statistical theory in a concise and accessible way to my peers. Writing the simulation and sharing conclusions will demonstrate my ability to implement statistical methods in practice as well as my ability to analyze the results of the simulation.

@@

# Exposition

The portion of the paper where you describe the new technique as though you were teaching it to a classmate (with whatever name you want to give it - Literature, Background, or Exposition) will be based on your annotated bibliography. You can add sources to what you already have in the annotated bibliography (especially if my feedback says you need to!). To be sure that you are on track with the exposition, a full draft of this portion of the paper is due before Thanksgiving break. This will also help with incorporating proper citation early in the writing process, as you’ll have a bibliography that we can implement for this portion of the paper at a minimum.

Exposition
-> what is a bootstrap
--> parametric
--> non-parametric
--> briefly: what is jackknife
--> SE and bias?
-> what is a bootstrapped confidence interval
--> what can it do
-> how do we create them
-> different types of bootstrapped CI
--> standard t interval, approx classical, swapped SE, percentile, Bias-corrected, BCa
---> for sample mean or corr (check example sheet)

Bootstrapping is a statistical method of resampling that allows the estimation of a test statistic from an unknown distribution. Supposing we have a random sample $X = (x_1,x_2,\dots,x_n)$, then the bootstrap sample could be represented as $X^* = (x^*_1, x^*_2, \dots, x^*_n)$ where each $x^*_i$ is sampled randomly with equal probability and with replacement from $\{x_1,x_2,\dots,x_n\}$. From this bootstrap sample, a bootstrap replication of the test statistic can be computed.

### 2022-11-17 project/PaperTemplate/paper.tex
Created copy of test paper
Edit on paper

  \author{
        XX YOUR NAME HERE XX \thanks{The authors gratefully acknowledge
\ldots{}} \\
    Department of Mathematics and Statistics, Amherst College\\
      }
  \maketitle
} \fi

@@

\bigskip
\begin{abstract}
The text of your abstract. 200 or fewer words. It is intended to provide
an overview of your paper and may be similar to your synopsis. Note that
an abstract can only include one paragraph in this format. You may want
to put your synopsis here as you work to refer to it easily.
\end{abstract}

@@

\begin{figure}
\centering
\includegraphics{test_files/figure-latex/sample-fig1-1.pdf}
\caption{\label{fig:sample-fig1}This is a sample figure caption that
should interpret the figure!}
\end{figure}

>>>>

  \author{
        Justin Papagelis \thanks{The authors gratefully acknowledge
\ldots{}} \\
    Department of Mathematics and Statistics, Amherst College\\
      }
  \maketitle
} \fi

@@

\bigskip
\begin{abstract}
For my project, I plan to explore different bootstrap methods for
creating confidence intervals and then perform comparisons between a
couple of the methods. My paper will re-introduce the idea of bootstrap
to my peers and give some background on constructing confidence
intervals. We will also go deeper into the theory behind the
construction of confidence intervals from bootstrapped data. These
various methods to create a confidence interval from a bootstrap can
include the percentile method, bias-corrected method, accelerated
method, and the studentized method, as well as others. I will
demonstrate how these bootstrap methods work using ``toy examples,''
which will be datasets in which a specific bootstrap method is
appropriate. To demonstrate my understanding of the methods, I will
write a simulation to compare a few of them and determine how they
perform against each other. I will show my understanding of the
different methods of creating confidence intervals from bootstrapped
data by communicating the statistical theory in a concise and accessible
way to my peers. Writing the simulation and sharing conclusions will
demonstrate my ability to implement statistical methods in practice as
well as my ability to analyze the results of the simulation.
\end{abstract}

@@

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/sample-fig1-1.pdf}
\caption{\label{fig:sample-fig1}This is a sample figure caption that
should interpret the figure!}
\end{figure}
